---
title: "KNN Classification Model with Binary Label"
author: "C"
date: "November 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Load Libraries
```{r}
library(ggplot2)
library(rpart)
library(class)
library(ROCR)
library(caret)
library(pROC)
setwd("~/GitHub/Final-Project/Three Models with Only Click Data Features [Binary Label]")
```
Load Data frame 


```{r}
df1 <- read.csv("AAA_Data_Binary_Label.csv")

```

Remove X variable

```{r}
df1 <- df1[,-c(1,3)]

```

Set seed

```{r}
set.seed(9850)

```

Generate random number to randomize data set

```{r}
gp <- runif(nrow(df1))

```

Mix the rows using the random number as the order

```{r}

df1_KNN <- df1[order(gp),]

```

create function to rescale/normalze the numeric features using max/min

```{r}
normalize <- function(x){
  return( (x - min(x)) / (max(x) - min(x)))}

```

Create new normalized data frame

```{r}

df1_KNN_n <- as.data.frame(lapply(df1_KNN[,c(2,3,4,5,6,7,8,9,10)], normalize))

```

Create training and test set and also create training and test targets. Use a .75 split ratio based on total number of observations (735 * .75 = 551 OR rows 1:552 for training set and rows 553:735 for test set.

```{r}
df1_KNN_train <- df1_KNN_n[1:552, ]
df1_KNN_test <- df1_KNN_n[553:735, ]
df1_KNN_train_target <- df1_KNN[1:552, 12]
df1_KNN_test_target <- df1_KNN[553:735, 12]

```

Calcualte the K value using cross-validated hyper perameter tuning script. 
```{r}
m1 <- knn(train = df1_KNN_train, test = df1_KNN_test, cl = df1_KNN_train_target, k=11, prob = TRUE)

```

build a confusion matrix to check the performance of the model

```{r}
confusionMatrix(m1, df1_KNN_test_target)
```

Visulaize results 

```{r}
knn_confusion <- as.data.frame(table(df1_KNN_test_target, m1))

knn_plot <- ggplot(knn_confusion)

knn_plot + geom_tile(aes(x=df1_KNN_test_target, y=m1, fill=Freq), color = "gray") + scale_x_discrete(name="Actual Class") + scale_y_discrete(name="Predicted Class") + scale_fill_gradient(high = "red") + labs(fill="Frequency", title = "KNN Confusion Matrix") + geom_text(data = knn_confusion, aes(x=df1_KNN_test_target, y=m1, label=Freq), color = "white")

```
visualize the performance of the model with an ROC curve using probabilies of predictions.

```{r}
knn_prob <- attr(m1, "prob")

```
The probabilitities come in a form that ROCR does not accept so we need to invert them for the -1 class and rescale them.

```{r}
prob <- 2*ifelse(m1 == "-1", 1-knn_prob, knn_prob) - 1
```
Feed the "probabilities" into the ROCR package's functions and obtain a ROC curve.

```{r}
pred_knn <- prediction(knn_prob, df1_KNN_test_target)
```
calculate model performance
```{r}
pred_knn <- performance(pred_knn, "tpr", "fpr")
```
Calculate AUC

```{r}
area <- auc(df1_KNN_test_target, knn_prob)
```
plot ROC

```{r}
rocplot <- function(knn_prob, df1_KNN_test_target, ...) {
  predob = prediction(knn_prob, df1_KNN_test_target)
  perf = performance(predob, "tpr", "fpr")
  plot(perf, ...)
  area <- format(round(area, 4), nsmall = 4)
  text(x=0.8, y=0.1, labels = paste("AUC =", area))
    segments(x0=0, y0=0, x1=1, y1=1, col="black", lty=2)
}
rocplot(knn_prob, df1_KNN_test_target, col="black", avg= "threshold", lwd=2, main="k-Nearest Neighbors ROC Curve")

```

