---
title: "Model Results"
author: "C"
date: "December 6, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Here we are comparing three seperate models that are trained using the same data set. The data set consists of click data from a VLE and a binary label of the over all student course outcome. As you can see, based on just using the interactiond ata as a predictor, the best KAPPA is .31 using the deciscion tree algorithm.

The next step is to introduce additional student features in an attempt to increase model accuracy using this same proccesses and algorithms.



```{r}
#########################
## Tree Classification ##
#########################
```

Confusion Matrix and Statistics

               Reference
Prediction       Monitor Don't Monitor
   Monitor            23            26
  Don't Monitor       22           113
                                         
               Accuracy : 0.7391         
                 95% CI : (0.6694, 0.801)
    No Information Rate : 0.7554         
    P-Value [Acc > NIR] : 0.7289         
                                         
                  Kappa : 0.3146         
 Mcnemar's Test P-Value : 0.6650         
                                         
            Sensitivity : 0.5111         
            Specificity : 0.8129         
         Pos Pred Value : 0.4694         
         Neg Pred Value : 0.8370         
             Prevalence : 0.2446         
         Detection Rate : 0.1250         
   Detection Prevalence : 0.2663         
      Balanced Accuracy : 0.6620         
                                         
       'Positive' Class :  Monitor       
       
       
       
```{r}
########################
## SVM Classification ##
########################
```
Confusion Matrix and Statistics

          Reference
Prediction ignore monitor
   ignore     125      38
   monitor      7      13
                                          
               Accuracy : 0.7541          
                 95% CI : (0.6851, 0.8146)
    No Information Rate : 0.7213          
    P-Value [Acc > NIR] : 0.1828          
                                          
                  Kappa : 0.2482          
 Mcnemar's Test P-Value : 7.744e-06       
                                          
            Sensitivity : 0.9470          
            Specificity : 0.2549          
         Pos Pred Value : 0.7669          
         Neg Pred Value : 0.6500          
             Prevalence : 0.7213          
         Detection Rate : 0.6831          
   Detection Prevalence : 0.8907          
      Balanced Accuracy : 0.6009          
                                          
       'Positive' Class : ignore          
       
```{r}
########################
## KNN Classification ##
########################
```
Confusion Matrix and Statistics

               Reference
Prediction       Monitor Don't Monitor
   Monitor            11             4
  Don't Monitor       37           131
                                          
               Accuracy : 0.776           
                 95% CI : (0.7086, 0.8342)
    No Information Rate : 0.7377          
    P-Value [Acc > NIR] : 0.1367          
                                          
                  Kappa : 0.2563          
 Mcnemar's Test P-Value : 5.806e-07       
                                          
            Sensitivity : 0.22917         
            Specificity : 0.97037         
         Pos Pred Value : 0.73333         
         Neg Pred Value : 0.77976         
             Prevalence : 0.26230         
         Detection Rate : 0.06011         
   Detection Prevalence : 0.08197         
      Balanced Accuracy : 0.59977         
                                          
       'Positive' Class :  Monitor        
