---
title: "Tree Classification Model with Binary Label"
author: "C"
date: "November 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Load Libraries
```{r}
library(ggplot2)
library(party)
library(rpart)
library(ROCR)
library(caret)
library(pROC)
setwd("~/GitHub/Final-Project/Three Models with Only Click Data Features [Binary Label]")
```

Load Data frame 

```{r}
df1 <- read.csv("AAA_Data_Binary_Label.csv")

```

Remove X Variable

```{r}

df1 <- df1[,-1]
```
set seed 

```{r}
set.seed(9850)

```

Generate random number to randomize data set

```{r}
gp <- runif(nrow(df1))

```

Mix the rows using the random number as the order

```{r}

df1 <- df1[order(gp),]

```


Split the data into a training set and test set (75% of data to training and 25 % of training to Test).

```{r}
n = nrow(df1)
train = sample(1:n, size = round(0.75*n), replace=FALSE)
df1.train = df1[train,]
df1.test = df1[-train,]
```

Build the decision tree

```{r}

tree <- ctree(factor(binary_label) ~ homepage + forumng + glossary + dataplus + oucollaborate + oucontent + resource + subpage + url, data=df1.train)

```

Plot the tree

```{r}

plot(tree)

```

Test the deciscion tree

```{r}
df1.test$prediction <- predict(tree, df1.test)

```

```{r}
c2.tree <- rpart(prediction ~ homepage + forumng + glossary + dataplus + oucollaborate + oucontent + resource + subpage + url, data=df1.test) 
printcp(c2.tree)
rpart(formula = prediction ~ homepage + forumng + glossary + dataplus + oucollaborate + oucontent + resource + subpage + url, data = df1.test, method = "class")
```

Check performance of the model using a confusion matrix

```{r}
confusionMatrix(df1.test$prediction, df1.test$binary_label)

```

Visulaize results 

```{r}
tree_confusion <- as.data.frame(table(df1.test$binary_label, df1.test$prediction))

tree_plot <- ggplot(tree_confusion)

tree_plot + geom_tile(aes(x=Var1, y=Var2, fill=Freq), color = "gray") + scale_x_discrete(name="Actual Class") + scale_y_discrete(name="Predicted Class") + scale_fill_gradient(high = "red") + labs(fill="Frequency", title = "Decision Tree Confusion Matrix") + geom_text(data = tree_confusion, aes(x=Var1, y=Var2, label=Freq), color = "white")

```
visualize the performance of the model with an ROC curve using probabilies of predictions.

```{r}
pred <- predict(tree, newdata=df1.test)
probs <- treeresponse(tree, newdata=df1.test)
pred <- do.call(rbind, probs)
summary(pred)
```

Extract pred
```{r}
pred1 <- pred[,2]
```

```{r}
area <- auc(df1.test$binary_label, pred1)
```
plot ROC

```{r}
rocplot <- function(pred1, df1.test, ...) {
  predob = prediction(pred1, df1.test$binary_label)
  perf = performance(predob, "tpr", "fpr")
  plot(perf, ...)
  area <- format(round(area, 4), nsmall = 4)
  text(x=0.8, y=0.1, labels = paste("AUC =", area))
    segments(x0=0, y0=0, x1=1, y1=1, col="black", lty=2)
}
rocplot(pred1, df1.test, col="black", avg= "threshold", lwd=2, main="Decision Tree ROC Curve")
```


