---
title: "KNN Classification Model with Binary Label"
author: "C"
date: "November 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Load Libraries
```{r}
library(ggplot2)
library(rpart)
library(class)
library(ROCR)
library(caret)
setwd("~/GitHub/Final-Project/Three Models with Click Data and Additional Features [Binary Label]")
```
Load Data frame 


```{r}
df1 <- read.csv("AAA_Data_Binary_Label_Additional_Features.csv")

```

Set seed

```{r}
set.seed(9850)

```

Generate random number to randomize data set

```{r}
gp <- runif(nrow(df1))

```

Mix the rows using the random number as the order

```{r}

df2 <- df1[order(gp),]

```
Remove unwanted features

```{r}
df1_KNN <- df2[,-c(1,2,3,14)]
```

Convert categorical features to integers 
```{r}
df1_KNN$gender = as.integer(df1_KNN$gender)
df1_KNN$region = as.integer(df1_KNN$region)
df1_KNN$highest_education = as.integer(df1_KNN$highest_education)
df1_KNN$imd_band = as.integer(df1_KNN$imd_band)
df1_KNN$age_band = as.integer(df1_KNN$age_band)
df1_KNN$disability = as.integer(df1_KNN$disability)

```

Replace NA Values in data frame

```{r}
df1_KNN[is.na(df1_KNN)] <- 0
```

Create data frame with label removed 
```{r}

df1_KNN_n <- df1_KNN[,-10]

```


Create training and test set and also create training and test targets. Use a .75 split ratio based on total number of observations (735 * .75 = 551 OR rows 1:552 for training set and rows 553:735 for test set.

```{r}
df1_KNN_train <- df1_KNN_n[1:552, ]
df1_KNN_test <- df1_KNN_n[553:735, ]
df1_KNN_train_target <- df1_KNN[1:552, 10]
df1_KNN_test_target <- df1_KNN[553:735, 10]

```

Calcualte the K value using the sqrt of the total number of observations sqrt(735) = 27.11088 and build the model using the knn function and training data.
```{r}
m1 <- knn(train = df1_KNN_train, test = df1_KNN_test, cl = df1_KNN_train_target, k=27, prob = TRUE)

```

build a confusion matrix to check the performance of the model

```{r}
confusionMatrix(m1, df1_KNN_test_target)
```

Visulaize results 

```{r}
knn_confusion <- as.data.frame(table(df1_KNN_test_target, m1))

knn_plot <- ggplot(knn_confusion)

knn_plot + geom_tile(aes(x=df1_KNN_test_target, y=m1, fill=Freq), color = "gray") + scale_x_discrete(name="Actual Class") + scale_y_discrete(name="Predicted Class") + scale_fill_gradient(high = "red") + labs(fill="Frequency", title = "KNN Confusion Matrix") + geom_text(data = knn_confusion, aes(x=df1_KNN_test_target, y=m1, label=Freq), color = "white")

```
visualize the performance of the model with an ROC curve using probabilies of predictions.

```{r}
knn_prob <- attr(m1, "prob")

```
The probabilitities come in a form that ROCR does not accept so we need to invert them for the -1 class and rescale them.

```{r}
prob <- 2*ifelse(m1 == "-1", 1-knn_prob, knn_prob) - 1
```
Feed the "probabilities" into the ROCR package's functions and obtain a ROC curve.

```{r}
pred_knn <- prediction(knn_prob, df1_KNN_test_target)
```
calculate model performance
```{r}
pred_knn <- performance(pred_knn, "tpr", "fpr")
```
plot ROC
```{r}
KNN_ROC <- plot(pred_knn, avg= "threshold", colorize=T, lwd=3, main="KNN Binary Label ROC Curve")
```


