---
title: "KNN Clasification Model"
author: "C"
date: "November 16, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Load Libraries
```{r}
library(ggplot2)
library(rpart)
library(class)
library(ROCR)
```

Set working directory 
```{r}
setwd("~/GitHub/Final-Project/Data Manipulation")
```


Load Data frame 


```{r}
df1 <- read.csv("AAA_Data_for_Tree.csv")

```

Remove X variable

```{r}
df1 <- df1[,-c(1,3)]

```

Set seed

```{r}
set.seed(9850)

```

Generate random number to randomize data set

```{r}
gp <- runif(nrow(df1))

```

Mix the rows using the random number as the order

```{r}

df1_KNN <- df1[order(gp),]

```

create function to rescale/normalze the numeric features using max/min

```{r}
normalize <- function(x){
  return( (x - min(x)) / (max(x) - min(x)))}

```

Create new normalized data frame

```{r}

df1_KNN_n <- as.data.frame(lapply(df1_KNN[,c(2,3,4,5,6,7,8,9,10)], normalize))

```

Create training and test set and also create training and test targets. Use a .75 split ratio based on total number of observations (735 * .75 = 551 OR rows 1:552 for training set and rows 553:735 for test set.

```{r}
df1_KNN_train <- df1_KNN_n[1:552, ]
df1_KNN_test <- df1_KNN_n[553:735, ]
df1_KNN_train_target <- df1_KNN[1:552, 11]
df1_KNN_test_target <- df1_KNN[553:735, 11]

```

Calcualte the K value using the sqrt of the total number of observations sqrt(735) = 27.11088 and build the model using the knn function and training data.
```{r}
m1 <- knn(train = df1_KNN_train, test = df1_KNN_test, cl = df1_KNN_train_target, k=11, prob = TRUE)

```

build a confusion matrix to check the performance of the model

```{r}
table(df1_KNN_test_target, m1)

```

Visulaize results with a confusion matrix

```{r}
knn_confusion <- as.data.frame(table(df1_KNN_test_target, m1))

knn_plot <- ggplot(knn_confusion)

knn_plot + geom_tile(aes(x=df1_KNN_test_target, y=m1, fill=Freq), color = "gray") + scale_x_discrete(name="Actual Class") + scale_y_discrete(name="Predicted Class") + scale_fill_gradient(high = "red") + labs(fill="Frequency", title = "KNN Confusion Matrix") + geom_text(data = knn_confusion, aes(x=df1_KNN_test_target, y=m1, label=Freq), color = "white")

```


